---
title: "HW04"
author: "Anton Zamyatin"
date: "4/10/2019"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Exploring data
```{r}

raw <- readRDS('weather.rds', refhook = NULL)

summary(raw) 
head(raw)
str(raw)
```
We noticed some issues:
1) "X" collumn is just an index
2) We must assign our samples as Year+month+day from X# columns
3) Divide mesure column into multiple columns

```{r}
# package include
library(tidyr)
library(stringr)
# get rid of X column
tidy <- raw[,-1]

# From wide to long
tidy <- gather(tidy, day, value, X1:X31)
# From long to wide
tidy <- spread(tidy, measure, value)

```

Next we recognised that some samples have all NAs data because of unexisting days and the end of the mesaures in the end of the table.

```{r}
tidy$day <- str_sub(tidy$day, 2, 3)
tidy <- unite(tidy, Date, year, month, day, sep = '_')
```

Next let`s get rid of empty samples from with NAs in dataframe(ends of  the months and end of the measurments)

```{r}
tidy <- na.omit(tidy)
```

Next format columns

```{r}
tidy$PrecipitationIn <- as.numeric(tidy$PrecipitationIn, na.string='T')
```

Make columns with numbers numeric

```{r}
tidy[,c(2,4:23)] <- lapply(tidy[,c(2,4:23)], as.numeric)
```

Once again look at the data:

```{r}
row.names(tidy) <- 1:nrow(tidy)
summary(tidy)
```

Make Events column factor

```{r}
tidy$Events <- as.factor(tidy$Events)
levels(tidy$Events)[1] <- "Common"
```

Lets look at plots of numeric columns

```{r}
boxplot(tidy[, c(2, 3:23)])
boxplot(tidy[, c(2, 3:22)])
```

We saw that Humidity has terrible outlier 1000% we think that this extra "0" at the end.

```{r}
tidy[135,6] <- 100
```

Thats all.

```{r}
head(raw)
head(tidy)
```





