---
title: "R Notebook"
output: html_notebook
---

Write a function that:

1 . Takes data frame, row selection and column selection as arguments

2. Subsets data according to the given selections. Possible selections are:

  By index/indexes

  By name/names

  By logical vector

3. For each column of the subsetted data performs some computations:

  For numeric data – any of sum(), mean(), sd(), etc. As you wish

  For non-numeric data (characters and logical vectors, factors) – frequency table

4. Returns an output as a data frame and calculation results as a list

```{r}
subset_df <- function(df, row_selection, column_selection){
  
  column_func <- function(x){
    if (is.numeric(x)){
      return(mean(x))
    } else {
      return(table(x))
    }
  }
  
  df_subs <- df[row_selection, column_selection, drop=F]
  d <- sapply(df_subs, column_func)
  
  return (list(df_subs, d))
}
```

Apply it in a few examples:

```{r}
library("datasets")
df <- mtcars
l <- subset_df(df, c(1,2,3), c(T, F))
l[[1]]
l[[2]]
```
```{r}
library("ggplot2")
df <- presidential
l <- subset_df(df, 1:10, c("name", "start", 'end'))
l[[1]]
l[[2]]
```


